Tampering Detection In Low-Power Smart Cameras

### 2015-05-19 paper.tex

\begin{algorithm}[tp]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{\mathcal{R}_k\}, k=1,\dots,K$ \\
	\textbf{Configuration}:\\
%	\lnl{DISPL-Tr1} Extract regions $\{\mathcal{R}_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Get frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $\mathcal{R}_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Compute $\sigma_l^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$ \\
		\lnl{DISPL-Test3} $n_l = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $\mathcal{R}_k$\\
			\lnl{DISPL-Test6} \If{$\partial l^k(t) < -\gamma \sigma_l^k \vee \partial l^k(t) > \gamma \sigma_l^k $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a tampered frame\\
		}
	}   
	\caption{Tampering detection algorithm}
	\label{alg:DISPL}
\end{algorithm}
\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

\section{Experiments}\label{sec:experiments}
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/buenosAires}
\caption{}
\label{fig:buenosAires}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/buenosAiresDef}
\caption{}
\label{fig:buenosAiresDef}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/fulvioTestiDispl}
\caption{}
\label{fig:fulvioTestiDispl}
\end{figure}

\subsection{Dataset Description}\label{subsec:Dataset}
\gi{Adriano: Prova a mettere qua le info}
The proposed method have been tested on a dataset of frame sequences in which there were tampering events.
A part of this dataset was taken using a Raspberry Pi with its camera module, and the tampering was introduced by moving the device or putting water on the camera.
The other part of this dataset is made of frame sequences taken from web-cams available on the Internet. 
In these sequences there were a few events of displacements or defocus, but to have a larger set of tampering events we
\subsection{Alternative Approaches}\label{subsec:AlternativeApproaches}
\begin{itemize}
\item Full
\item Adaptive Region
\item Voronoi Regions
\end{itemize}

>>>>

\begin{algorithm}[tp]
	% \SetAlgoNoLine
	\LinesNumbered
	\SetAlgoNlRelativeSize{0}
	\SetNlSty{small}{}{.}
	\textbf{Input}: $\gamma$, $T_{o}$, $\{R_k\}, k=1,\dots,K$ \\
	\textbf{Configuration}:\\
%	\lnl{DISPL-Tr1} Extract regions $\{\mathcal{R}_k\}, k=1,\dots,K$  \\
	\lnl{DISPL-Tr2} \For{$t=1,\dots,T_{o}$}
	{	\lnl{DISPL-Tr3} Get frame $z_t$ \\
		\lnl{DISPL-Tr4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Tr5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
		}
	}
	\lnl{DISPL-Tr6} \For{$k=1,\dots,K$}{
		\lnl{DISPL-Tr7} Compute $\sigma_l^k$\\
	}
	\textbf{Operational phase}:\\
	\lnl{DISPL-Test1} \For{$t=T_{o},\dots,\infty$}{
		\lnl{DISPL-Test2} Get frame $z_t$ \\
		\lnl{DISPL-Test3} $n_l = 0$ \\
		\lnl{DISPL-Test4} \For{$k=1,\dots,K$}{
			\lnl{DISPL-Test5} Compute $l^k(t)$, $\partial l^k(t)$ for the region $R_k$\\
			\lnl{DISPL-Test6} \If{$\partial l^k(t) < -\gamma \sigma_l^k \vee \partial l^k(t) > \gamma \sigma_l^k $}{
				\lnl{DISPL-Test7} $n_l=n_l+1$\\
			}
		}
		\lnl{DISPL-Test8} \If{$n_l\geq K-1$}{
			\lnl{DISPL-Test9} $z_t$ is a tampered frame\\
		}
	}   
	\caption{Tampering detection algorithm}
	\label{alg:DISPL}
\end{algorithm}
%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}

\section{Experiments}\label{sec:experiments}
The proposed algorithm has been implemented in MATLAB, and has been tested on two datasets.
The first one refers to frame sequences taken from webcams recording some parts of cities (as frames illustrated in Figure \ref{fig:buenosAires}), where we have introduced some synthetically generated tampering events:
defocus has been simulated using gaussian filters, while displacement has been created with concatenation of similar frame sequences.
\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{Immagini/buenosAires}
	\caption{Example of frame sequence taken from webcam. Frames have been acquired every $30$ seconds.}
	\label{fig:buenosAires}
\end{figure}
\begin{figure}
\centering
\subfigure[]{\label{fig:buenosAiresDef} \includegraphics[width=1\linewidth]{Immagini/buenosAiresDef}}
\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=1\linewidth]{Immagini/buenosAiresDispl}}
\caption{Examples of synthetically generated tampering events. \textbf{(a)} Defocus generated with gaussian filters on frames \textit{d} and \textit{e}. \textbf{(b)} Displacement created doing concatenation of similar sequences on frames \textit{d} and \textit{e}.}
\label{fig:buenosAiresTamp}
\end{figure}
In some cases these sequences contained real tampering events, as in Figure \ref{fig:fulvioTestiDispl}.\\
\begin{figure}
\centering
\includegraphics[width=1\linewidth]{Immagini/fulvioTestiDispl}
\caption{Example of sequence taken from webcam in which there is a real displacement (frame \textit{d})}
\label{fig:fulvioTestiDispl}
\end{figure}
The second dataset was taken using a Raspberry Pi Model B+, with its camera module, and the tampering was introduced by moving the device or putting water on the camera.\\
Four figures of merit have been suggested to assess the performance of the proposed algorithm:\\
\begin{description}
	\item[TP]  True positives. It measures the number of tampering events correctly detected by the algorithm.\\ 
	\item[TN]  True negatives. It measures the number of frames without tampering that are not detected by the algorithm. \\ 
	\item[FP]  False positives. It measures the number of tampering events erroneously detected by the algorithm.\\ 
	\item[FN]  False negatives. It measures the number of tampering events not detected by the algorithm. \\ 
\end{description} 
These indicators are computed varying the parameter $\gamma$, which defines the thresholds for the one-shot monitoring. 
This permits us to generate \textit{ROC curves}, where on the x-axis there is:
\[1-\text{SPECIFICITY}_\gamma = 1-\frac{\text{TN}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}=\frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma},\]
while on th y-axis there is:
\[\text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
The construction of these curves permits us to

\subsection{Alternative Approaches}\label{subsec:AlternativeApproaches}
\begin{itemize}
\item Full
\item Adaptive Region
\item Voronoi Regions
\end{itemize}
